### 2016-01-27 hans/bayes-tardis-luminosity-prediction.tex
[hans] expand gamma subsection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Bayesian prediction of luminosity distribution based on one simulation run:
% An example from TARDIS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage[a4paper, left=20mm, right=20mm, top=25mm, bottom=25mm]{geometry}

\usepackage[colorinlistoftodos]{todonotes} % Use 'disable' to remove todos in final version
\newcommand{\fred}[1]{\todo[inline]{#1}} %
\newcommand{\checked}[1]{\todo[color=green,noline]{\checkmark}} %
\newcommand{\checkedl}[1]{\todo[color=brown]{\checkmark}} %

@@

\DeclareMathOperator{\GammaDist}{Gamma}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{kendall}Stuart and Ord, \textit{Kendall's Advanced Theory of Statistics},
  Vol. 1, 5th Edition etc..

\end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Bayesian prediction of luminosity distribution based on one simulation run:
% An example from TARDIS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage[a4paper, left=20mm, right=20mm, top=25mm, bottom=25mm]{geometry}
\usepackage[numbers]{natbib}

\usepackage[colorinlistoftodos]{todonotes} % Use 'disable' to remove todos in final version
\newcommand{\fred}[1]{\todo[inline]{#1}} %
\newcommand{\checked}{\todo[color=green,noline]{\checkmark}} %
\newcommand{\checkedl}{\todo[color=brown]{\checkmark}} %

@@

\DeclareMathOperator{\GammaDist}{Gamma}
\newcommand{\refeq}[1]{Eq.~(\ref{#1})}

@@

With $\bmphi = (\alpha, \beta)$, the property \refeq{gmb} is
equivalent to
\begin{align}
  \lleq{gmc}
 p(L \cond N, \bmphi) &= \int d\bmL\,\delta(L - \textstyle\sum_j L_j)
  \,p(\bmL\cond N,\bmphi) = Gamma(L \cond N \alpha, \beta)
\end{align}
and this implies that the master equation~(\ref{pmp}) considerably simplifies as
\begin{align}
  \lleq{gmd}
    p(L\cond n,\bml,m)
  = \frac{1}{p(\bml\cond n)}
  \sum_N p(N\cond n)\, \int d\bmphi\, p(L \cond \bmphi)\, p(\bml\cond m,\bmphi)
  \, p(\bmphi).
\end{align}

To explicitly evaluate \refeq{gmd}, we have to overcome the remaining
two difficulties: the sum over $N$ and the integral over
$\bmphi$. Regarding the latter, there is a conjugate prior but
unfortunately the normalization constant can not be evaluated in
closed form. It is thus of no use for us, and we turn to a
noninformative prior. In \cite{Moala:2013}, an overview of possible
choices is given. They conclude that the point estimate given by the
mode of the posterior is nearly insensitive to the prior choice for 30
samples. We require in addition that the posterior is narrow enough so
we group samples in bins to have at least $m=150$ samples in each
bin. The following approximations can be used in different regions of
the parameter space spanned by $n$ and $m$.

\begin{enumerate}
  \item
\end{enumerate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{references}
